### 2024-11-05 README.Rmd
update Readme

## General notes on naming data files

@@

- Default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
- "ho" suffix: holdout data (target years 2013-2023)
- "directional" suffix: directional error method
- "oecd" prefix: OECD truth data (used for robustness check)
- "to_score" prefix: excludes some instances for scoring data. All scores in scores/ folder are calculated based on these data versions.

>>>>

## General notes on the naming of data files

@@

- default setting: training data (target years 2001-2012); absolute error method; IMF WEO truth data; complete data before discarding instances for scoring
- "ho" suffix: holdout data (target years 2013-2023)
- "directional" suffix: directional error method
- "oecd" prefix: OECD truth data (used for robustness check)
- "to_score" prefix: excludes some instances for scoring data. All scores in scores/ folder are calculated based on these data versions.
- "bvarspecs" prefix: for scoring different BVAR specifications (benchmark models) against each other. Excludes more instances, for data availability reasons.

## Contents of individual folders
